---
title: "shortRNA"
output: 
  xaringan::moon_reader:
    seal: false
    libs: libs
    css: ["css/xaringan.css", "default", "default-fonts"]
    nature:
      ratio: '16:9'
      beforeInit: ["addons/macros.js", "https://platform.twitter.com/widgets.js"]
      highlightLines: true
      highlightSpans: false
      highlightStyle: github
      countIncrementalSlides: false
      countdown: false
      slideNumberFormat: '%current%'
      navigation:
        scroll: false
editor_options: 
  chunk_output_type: console
---

class: inverse, middle, center

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.duplicate.label = "allow")
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
```

```{r xaringan-tile-view, echo=FALSE, warning=FALSE, message=FALSE}
xaringanExtra::use_tile_view()
xaringanExtra::use_animate_css()
xaringanExtra::use_panelset()
xaringanExtra::use_tachyons()
# xaringanExtra::style_panelset(panel_tab_color_active = "red")
xaringanExtra::style_panelset(
  panel_tab_color_active = "#0051BA",
  panel_tab_color_hover = "#d22",
  panel_tab_font_family = "Roboto"
)
```

```{r xaringan-logo, echo=FALSE}
xaringanExtra::use_logo(
  image_url = "files/p1/logo.png",
  link_url = "https://github.com/mansuylab/shortRNA",
  position = xaringanExtra::css_position(top = "1em", right = "1em")
)
```


<br>

# .orange[`shortRNA`: A flexible framework for the analysis of short RNA sequencing data]


## 24<sup>th</sup> February, 2022

## Deepak Kumar Tanwar

### `r anicon::faa("envelope", animate="", colour = "#2395fb")` [.red1[dktanwar@hotmail.com]](mailto:dktanwar@hotmail.com)
### `r anicon::faa("twitter", animate="", colour = "#00acee")` [.red1[@d_k_tanwar]](https://twitter.com/d_k_tanwar)


---

```{r child='p2.Rmd'}
```

---

```{r child='p3.Rmd'}
```

---

```{r child='p4.Rmd'}
```

---

```{r child='p5.Rmd'}
```

---


class: center, middle, hide_logo

.eLarge[.blue[**Thank you for your attention!**]]
